---
title: "homework-2"
format: pdf
editor: visual
---

# Packages

## Question 1

```{r}
#| eval: FALSE
install.packages("aRtsy")
```

The difference between install.packages and library is that install.packages downloads a package to the computer while library loads an already-installed package into the current session.

\newpage

## Question 2

```{r}
library("aRtsy")
```

The Collatz Conjecture is a famous unsolved math problem that asks whether repeating two simple rules will always reach the number 1 for any positive whole number.

If the number is even, divide it by 2 until you get 1. For example, $4/2 = 2/2 = 1$ If the number is odd, multiply by 3, add by 1, and use the previous property until you get 1. For example, $1 * 3 + 1 = 4/2 = 2/2 = 1$

\newpage

## Question 3
#### Part A
```{r}
canvas_collatz(
  colors = c("blue"),
  n = 10
)
```
This canvas_collatz function creates 10 blue lines on a blank "canvas" on the computer. These lines probably involve those Collatz Equations. Maybe it traces the path of 10 numbers using the Collatz equations. 

#### Part B
1) You get a different output everytime you run the code because the function randomly chooses 10 numbers for the starting points. 
2) This is difficult because everytime I render the document, the artwork will change. This potentially messes up my description of the artwork. 

```{r}
?set.seed # By giving it a fixed number, you force the random number generator to start at the exact spot every time, creating the same artwork. 
set.seed(67)
```

\newpage

## Question 4

```{r}
canvas_collatz(
  colors = c("blue"),
  n = 10
)
```
```{r}
canvas_collatz(
  colors = c("blue"),
  n = 1:20
)
```
The first code randomly chooses any 10 integers while the second code uses the numbers 1 through 20. The second code always produces the same artwork while the second  
